\LARGE \bf Artifical Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-16 paper.tex
Fixing language 8

The challenge of symbol grounding is also tightly linked to this issue. It
corresponds to the identification or creation, and then, maintenance of a link
between the symbol (the syntactic form of knowledge that the computer
manipulates) and its semantics, \ie its meaning, anchored in the world (the
relations between the symbol, the referent of the symbol, and mediating minds
is classically referred as the \emph{semantic triangle} and has been
extensively studied in linguistics). The issue of grounding is well known in
cognitive science and is summarised by Harnard~\cite{Harnad1990} by this
question: ``how the semantic interpretation of a formal symbol system can be
made intrinsic to the system?''. This issue has a major practical importance in
robotic: for a robot to be both endowed with a symbolic representational and
reasoning system, and able to \emph{act} in the physical world, it must ground
its knowledge.

@@

Grounding also occurs during verbal and non-verbal communication. The {\sc
Dialogs} module grounds new concepts introduced by the speaker by asking
questions until it can attach the new concept to concepts already present in the
knowledge pool (typically, if I ask the robot ``bring me a platypus'', the robot
asks ``what is a platypus''. I may answer ``a mammal'' and the robot will ask
``what is a mammal?'' and so on until it anchors the new concepts to ones it
already knows). Embodied interactions (like gestures) are also taken into
account at this level: we have presented how pointing, for instance, is used by
the robot to ground \emph{``this''} or \emph{``that''} to the pointed artifact.

Note that because only objects marked with 2D fiducial markers are currently
recognised (in our typical lab experiments, it may be a dozen of them), the
robot's grounding mechanisms only work in a small-sized closed world. This
assumption greatly facilitates the task, and we see that we have only scratched
the surface of a generic grounding capability. Context, cultural background,
``naive physics'' knowledge, emotional state of the human are some of the
numerous other determinants that need to be accounted for when grounding
human-robot interaction.

@@

While the task of describing all the (dynamic!) human models that are useful to
robots is immense (if doable at all), we claim that it is possible to devise and
use such models in limited, but still interesting and useful, contexts such as
collaborative human-robot objects manipulation, fetch-and-carry and associated
activities in home or work environment.

In our implementation, perspective taking, for instance, is tightly connected to
the symbolic knowledge models, and since our knowledge base allows for storage
of one knowledge model per agent, we have been able to endow the robot with a
simple theory of mind (as explained in section~\ref{sect|tom}): we explicitly
model what the robot knows about its partners in a symbolic way. This knowledge
is then re-used in different places, to correctly interpret what the human says,
or to plan tasks that are actually doable for the human.

The cognitive model that the robot builds for the agents it interacts with
remains today simple and mostly focused on geometric features and affordances
(\emph{who sees what? what are our relative positions? what is reachable to
whom?}  etc.). Extending this knowledge with more subtle perceptions (emotional
state for instance) remains to be done.

@@

\subsection{Knowledge and Robotics}
\label{krs-discussion}

As thoroughly presented in this article, we have built the decisional
capabilities of our robots around this idea of explicit knowledge manipulation.
We finally briefly comment on this design choice and the limitations that we
have observed.

\subsubsection{Knowledge and Architecture}

As a whole, the components that we have introduced so far build a
knowledge-oriented architecture: knowledge is explicitly stored in one central
and consistent repository of facts, accessible for all modules. It relies on a
strict formalism (OWL statements), with a well defined vocabulary
(stated in the common-sense ontology). These first two points lead to a
\emph{loosely-coupled architecture} where modules can be removed or replaced
easily by other ones as long as they share the same semantics (modules are
defined by the knowledge they produce).

Also, we adopt a symbolic, reactive, event-driven approach to robot control. By
managing events at the same level as the reasoner, we take full advantage of the
inference abilities of {\sc Oro} to trigger events whose \texttt{true}
conditions can be (possibly indirectly) inferred.

And finally, this architecture allows for the combination of very different
knowledge sources in a single homogeneous environment, bringing mutual
benefits to components. For instance, the dialogue processing module can
run without any situation assessment, but its disambiguation routines
can transparently benefit from it when available (since richer symbolic
descriptions of objects are then available).

Those items are not new \emph{per se}. It is however interesting to underline
the shift of focus this implies during the design and integration phases of
robots: components of our deliberative layer are defined and glued together by
the knowledge they produce and consume. Human-robot interaction, because it
supposes operations at \emph{human-level} and in environments with complex
semantics, acts here as a motivational force.

>>>>

The challenge of symbol grounding is also tightly linked to this issue. It
corresponds to the identification or creation, and then, maintenance of a link
between the symbol (the syntactic form of knowledge that the computer
manipulates) and its semantics (its meaning, anchored in the world). The
relations between the symbol, the referent of the symbol, and mediating minds
is classically referred as the \emph{semantic triangle} and has been
extensively studied in linguistics. The issue of grounding is well known in
cognitive science and is summarised by Harnard~\cite{Harnad1990} by this
question: ``how the semantic interpretation of a formal symbol system can be
made intrinsic to the system?''. This issue has a major practical importance in
robotic: for a robot to be both endowed with a symbolic representational and
reasoning system, and able to \emph{act} in the physical world, it must ground
its knowledge.

@@

Grounding also occurs during verbal and non-verbal communication. The {\sc
Dialogs} module grounds new concepts introduced by the speaker by asking
questions until it can attach the new concept to concepts already present in the
knowledge pool (if one asks the robot ``bring me a margarita'', the robot may
initially asks ``what is a margarita?''. The user would answer ``a cocktail''
and the robot would continue the grounding -- ``what is a cocktail?'' -- until
it anchors the new concept to ones it already knows). Embodied interactions
(like gestures) are also taken into account at this level: we have presented how
pointing, for instance, is used by the robot to ground \emph{``this''} or
\emph{``that''} to the pointed artifact.

Note that, because only objects marked with 2D fiducial markers are currently
recognised (typically, about ten of them are simultaneously used in a given
experiment), our grounding mechanisms have only been exercised in small-sized
closed world. This simplifies the task, and we can not claim that our approach
provides a generic grounding capability. Beyond the perception of geometric
entities, context, cultural background, ``naive physics'' knowledge, emotional
state of the human are some of the numerous other determinants that need to be
accounted for when grounding human-robot interaction.

@@

While the task of describing all the (dynamic!) human models that are useful to
robots is immense (if doable at all), we claim that it is possible to devise and
use such models in limited, but still interesting and useful, contexts such as
collaborative human-robot objects manipulation, fetch-and-carry and associated
activities in home or work environments.

In our architecture, perspective taking, for instance, is tightly connected to
the symbolic knowledge models, and since our knowledge base allows for storage
of one knowledge model per agent, we have been able to endow the robot with a
simple theory of mind (as explained in section~\ref{sect|tom}): we explicitly
model what the robot knows about its partners in a symbolic way. This knowledge
is then re-used in different places, to correctly interpret what the human says,
or to plan tasks that are actually doable for the human.

The cognitive model that the robot builds for the agents it interacts with
remains today simple and mostly focused on geometric features and affordances
(\emph{who sees what? what are our relative positions? what is reachable to
whom?}). Extending this knowledge with more subtle perceptions (emotional
state for instance) remains to be explored beyond simple examples like the
processing of explicit verbal statements like ``I'm tired!''
(Section~\ref{sect:desires}).

@@

\subsection{Explicit Knowledge for Social Robotics}
\label{krs-discussion}

As thoroughly presented in this article, we have built the decisional
capabilities of our robots around this idea of explicit knowledge manipulation.
We finally briefly comment on this design choice and the limitations of our
approach.

\subsubsection{Explicit Knowledge in our Architecture}

The components that we have presented so far build a \emph{knowledge-oriented}
architecture: knowledge is explicitly stored in one central and consistent
repository of facts, accessible for all modules. It relies on a strict formalism
(OWL statements), with a well defined vocabulary (stated in the common-sense
ontology). These first two points lead to a loosely-coupled architecture
where modules can be removed or replaced easily by other ones as long as they
share the same semantics: modules are defined by the knowledge they produce or
consume.

Also, we adopt a symbolic, hybrid (reactive and planning-based), event-driven
approach to robot control. By managing events at the same level as the reasoner,
we take full advantage of the inference abilities of {\sc Oro} to trigger events
whose \texttt{true} conditions can be (possibly indirectly) inferred using
human-level semantics.

And finally, this architecture allows for the combination of different
knowledge sources in a uniform model, bringing mutual
benefits to components. For instance, the dialogue processing module can
run without any situation assessment, but its disambiguation routines
can transparently benefit from it when available (since richer symbolic
descriptions of objects are then available).

Those characteristics are not novel \emph{per se}. We want however underline the
shift of focus brought by this approach during the design and integration phases
of robots: components of our deliberative layer are defined and bound together
by the knowledge they produce and consume. Human-robot interaction, because it
supposes operations at \emph{human-level} and in environments with complex
semantics, acts here as a motivational force.
